### 2019-04-05 papers/journal/problem.tex
removed unwanted refernce

\noindent This section will present the different search problems of VTS.
%
We categorize the search problem, Figure~\ref{fig:vts-search} into three different categories, search problem for existential condition, search problem for universal condition, and performing synthesis on the incomplete VTS. 
%
We will present Figure~\ref{fig:vts-search}, two encodings for existential condition and one each for universal condition condition and synthesis.

@@

\begin{tikzpicture}
\begin{customlegend}[legend columns=-1,legend style={draw=none,column sep=1ex},legend entries={ \small Problem Statement, \small Encodings}]
\addlegendimage{fill=fv,area legend} 
\addlegendimage{fill=ai,area legend} 
%\addlegendimage{fill=ar,area legend}
%\addlegendimage{red,fill=black!50!red,ybar,ybar legend}
\end{customlegend}
\end{tikzpicture}

@@

We will do synthesis against the property that the VTS
is stable and 3-connected.
%
% The property is designed to balance the search space such that the synthesis procedure does not
% succeed with simply adding too many edges. 
%
%\begin{align*}
%\texttt{Property} =  \texttt{Stability} \land \texttt{Connected}(3) 
%%\land \texttt{DisConnected}(4)
%\end{align*}
This property was proposed in~\cite{shukla2017discovering}.
%
However, the biological relevance of the property is debatable and open for change.
%
% Our tool is easily modifiable to support any other property that may be deemed 
% interesting by the biologists.

>>>>

\noindent This section will present the different search problems of VTS.
%
We categorize the search problem, Figure~\ref{fig:vts-search} into three different categories, search problem for existential condition, search problem for universal condition, and performing synthesis on the incomplete VTS. 
%
We will present two encodings for existential condition and one each for universal condition condition and synthesis.

@@

\begin{tikzpicture}
\begin{customlegend}[legend columns=-1,legend style={draw=none,column sep=1ex},legend entries={ \small Search Problems, \small Encodings}]
\addlegendimage{fill=fv,area legend} 
\addlegendimage{fill=ai,area legend} 
%\addlegendimage{fill=ar,area legend}
%\addlegendimage{red,fill=black!50!red,ybar,ybar legend}
\end{customlegend}
\end{tikzpicture}

@@

We will do synthesis against the property that the VTS
is stable and k-connected (k=3,4).
%
% The property is designed to balance the search space such that the synthesis procedure does not
% succeed with simply adding too many edges. 
%
%\begin{align*}
%\texttt{Property} =  \texttt{Stability} \land \texttt{Connected}(3) 
%%\land \texttt{DisConnected}(4)
%\end{align*}
This property was proposed in~\cite{shukla2017discovering}.
%
However, the biological relevance of the property is debatable and open for change.
%
% Our tool is easily modifiable to support any other property that may be deemed 
% interesting by the biologists.
